A linearization procedure for constrained multibody systems

### 2012-08-28 PetersonGedeHubbard2012.tex
Revised a couple sentences in example.

The matrices which make up the linear equations were created using the method
presented in Section \ref{sec:results}. It is very important to note that the
quantities in the matrices represent the states at the point of linearization.
This leads to $q$'s, $u$'s, $\dot{q}$'s, and $\dot{u}$'s all showing up. The
nonlinear equations need to be evaluated at a point to determine all of these
quantities. The $\dot{u}$ quantities are not actually required to be 0, so
equilibrium is not a requirement of the linearization point chosen. To reduce
the complexity of the equations, we chose $q_0$ and $q_2$ to be equal to 0.
This means that the other quantities in the linearized equations (other $q$'s,
the $\dot{q}$'s, the $u$'s, and the $\dot{u}$'s need to be solved for with
these 2 quantities already set to 0).

>>>>

The matrices which make up the linear equations were created using the method
presented in Section \ref{sec:results}. It is important to note that the
entries in these matrices must be evaluated at the point of linearization
($\bm{q}^*, \bm{\dot{q}}^*, \bm{u}^*, \bm{\dot{u}}^*$), and that this point of
linearization must satisfy the equations in Table \ref{table:assumptions}.
There is no requirement that this point be an equilibrium point, which implies
that in general both $\bm{\dot{q}}$ and $\bm{\dot{u}}$ may be non-zero. To
reduce the complexity of the equations, we chose $q_0^* = q_2^* = 0$.  This
means that the other quantities in the linearized equations (other $q$'s, the
$\dot{q}$'s, the $u$'s, and the $\dot{u}$'s need to be solved for with these 2
quantities already set to 0).
